---
title             : "Effect of Interactivity on Donation Intention: Mediated Roles of Playfulness, Social Presence, Sympathy, and Perceived Response Efficacy"
shorttitle        : "Effect of Interactivity on Donation Intention"

author: 
  - name          : "Zhanming Chen"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Department of Design Innovation, University of Minnesota, 89 Church Street SE, Minneapolis, MN 55455, USA"
    email         : "chen8475@umn.edu"
    role: # Contributorship roles (e.g., CRediT, https://credit.niso.org/)
      - "Conceptualization"
      - "Methodology"
      - "Project administration"
      - "Visualization"
      - "Writing - Original Draft"
      - "Writing - Review & Editing"

affiliation:
  - id            : "1"
    institution   : "University of Minnesota"

authornote: |
  I want to thank Professor Moin Syed for his guidance and hands-on lectures, as well as all the students in PSY 8960 for their help and feedback.
  

abstract: |
  Interactive advertising can improve consumers' purchase intentions, but its effectiveness in promoting donation behaviors is less explored. This study investigates the relationship between perceived interactivity and donation intention. Data were collected from 600 MTurk participants through a between-subject experimental design. Our findings indicate that perceived interactivity positively affects donation intention. Furthermore, this influence is mediated by perceived playfulness, sympathy, social presence, and perceived response efficacy. 
  
keywords          : "interaction design, advertising, donation, behavior"
wordcount         : "1190" # NOTE: update here before submission

floatsintext      : yes
linenumbers       : no
draft             : no
mask              : no

figurelist        : no
tablelist         : no
footnotelist      : no

classoption       : "man"
output            : papaja::apa6_pdf 
bibliography: ["references.bib", "r-references.bib"]
---

```{r setup, include = FALSE}
# optional: installed XQuartz package to enable “summaryTools”
library(papaja)
library(groundhog)
library(dplyr)
library(psych)
library(labelled)
library(ggplot2)
r_refs("r-references.bib")
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(1997)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

```{r data setup, include=FALSE}
dat_sim <- read.csv("../Data/interactive_ads_data_simulated_sample_20251125.csv")
# update this line as the following one if you only download this file and the dataset csv file
# dat_sim <- read.csv("interactive_ads_data_simulated_sample_20251125.csv")
names(dat_sim)
```

As one of the emerging forms of advertising, interactive advertising adds features to traditional advertising that allow consumers to interact with and participate in the ads [@bezjian-avery1998]. These interactive features provide active control, two-way communication, and a sense of synchronous reaction for the audience during interaction [@liu2002; @lombard2001; @mcmillan2002]. Traditional advertising, such as static image ads in shopping malls, provided a one-way channel for delivering marketing information to the audience in a controlled, linear narrative. Compared to traditional advertising, interactive advertising has been shown to increase both consumers’ attitudes and purchase intentions [@macias2003] and further improve overall marketing performance [@gu2022]. An example of interactive advertising was the 2015 augmented-reality-based ad launched by Coca-Cola in the United States, titled “Next time you’re thirsty, drink an ad” [@dipdropbrandingsolution2015]. During basketball games, viewers could enjoy a visual experience of a smooth transition from TV to mobile devices, as they watched Coke Zero being poured from a bottle on the TV screen into a glass in the mobile app. Coca-Cola then offered a coupon code redeemable for a bottle of Coke Zero [@thecoca-colacompany2015].

While previous research on interactive advertising has focused on its effects on consumption behaviors [e.g., @ahn2024], the impact of interactive advertising on donation intentions and behaviors has been minimally explored. In this study, we aim to understand how interactive advertisements influence donation attitudes and behaviors. Therefore, our research question is: how does the level of advertising interactivity impact the audience’s donation intentions?

## The Present Study

Research has shown that interactive design features of advertisements (e.g., buttons and body gestures) contribute to higher purchase intention [@ahn2024; @gu2022]. At the same time, the perceived interactivity of visual materials can positively influence the audience’s emotions, such as perceived playfulness, levels of sympathy, and social presence [@kang2020; @hand2009; @ide2021]. Furthermore, the audience’s positive emotions, including perceived playfulness, sympathy, and social presence, were examined separately and shown to affect perceptions of efficacy and behavioral intentions [@chen2019; @kim2015]. Additionally, researchers identified perceived response efficacy, the belief that consumers’ help can make a meaningful difference for beneficiaries [@sharma2016; @septianto2021], as an important factor in explaining donation behaviors.

Building on the prior research, we propose the following five hypotheses (H1–H5):

-   H1. Perceived interactivity of advertisements will be positively related to (a) perceived playfulness, (b) level of sympathy, and (c) social presence.
-   H2. Perceived playfulness will be positively related to (a) perceived response efficacy and (b) donation intention.
-   H3. Level of sympathy will be positively related to (a) perceived response efficacy and (b) donation intention.
-   H4. Social presence will be positively related to (a) perceived response efficacy and (b) donation intention.
-   H5. Perceived efficacy will be positively related to donation intention.

# Method

We conducted a between-subjects online experiment with two groups: high-interactivity and low-interactivity (controlled group). The stimulus is designed as an ad that encourages participants to donate winter clothing to a local homeless girl. For interactive features, participants in two groups either used a drag-and-drop feature to “donate” three pieces of clothing (i.e., high-interactivity) or watched an animation of the giving process for those three pieces of clothing (i.e., low-interactivity). 

The current study was **NOT** preregistered. Simulated data and codes are available at [OSF](https://osf.io/ept28/files) and [GitHub](https://github.com/zhanmingchen/PSY8960-Fall25-Zhanming).

## Participants and Procedure

```{r demographics, include=FALSE}

# create objects for mean and sd of age, to be inserted in text
age_sim_mean <- round(mean(dat_sim$age_sim), 2)
age_sim_sd <- round(sd(dat_sim$age_sim), 2)

# gender: recode gender factors from (1, 2) to (Male, Female, Non-binary or third gender, Prefer not to say)
dat_sim <- mutate(dat_sim, gender_sim = factor(gender_sim, levels = c(1, 2, 3, 4), 
                                           labels = c("Male", "Female", "Non-binary or third gender", "Prefer not to say")))
summarytools::freq(dat_sim$gender_sim)

# gender: creating object for percent, to include in descriptives and the table
female_sim_percent <- round((nrow(filter(dat_sim, gender_sim == "Female"))/(nrow(dat_sim)) * 100), 2)
nonbin_sim_percent <- round((nrow(filter(dat_sim, gender_sim == "Non-binary or third gender"))/(nrow(dat_sim)) * 100), 2)
male_sim_percent <- round((nrow(filter(dat_sim, gender_sim == "Male"))/(nrow(dat_sim)) * 100), 2)

# gender: creating object for frequency, to include in the table 
female_sim_count <- length(which(dat_sim$gender_sim == "Female"))
nonbin_sim_count <- length(which(dat_sim$gender_sim == "Non-binary or third gender"))
male_sim_count <- length(which(dat_sim$gender_sim == "Male"))

# recode race factors from (1, 7) to (White, Black or African American, American Indian or Alaska Native, Asian, Native Hawaiian or Pacific Islander, Other please specify, Prefer not to say)
dat_sim <- mutate(dat_sim, race_sim = factor(race_sim, levels = c(1, 2, 3, 4, 5, 6, 7), 
                                           labels = c("White", "Black or African American", "American Indian or Alaska Native", "Asian", "Native Hawaiian or Pacific Islander", "Other please specify", "Prefer not to say")))
summarytools::freq(dat_sim$race_sim)

# race: creating object for percent, to include in descriptives and the table
white_sim_percent <- round((nrow(filter(dat_sim, race_sim == "White"))/(nrow(dat_sim)) * 100), 2)
black_sim_percent <- round((nrow(filter(dat_sim, race_sim == "Black or African American"))/(nrow(dat_sim)) * 100), 2)
indian_sim_percent <- round((nrow(filter(dat_sim, race_sim == "American Indian or Alaska Native"))/(nrow(dat_sim)) * 100), 2)
asian_sim_percent <- round((nrow(filter(dat_sim, race_sim == "Asian"))/(nrow(dat_sim)) * 100), 2)
islander_sim_percent <- round((nrow(filter(dat_sim, race_sim == "Native Hawaiian or Pacific Islander"))/(nrow(dat_sim)) * 100), 2)

# race: creating object for frequency, to include in the table 
white_sim_count <- length(which(dat_sim$race_sim == "White"))
black_sim_count <- length(which(dat_sim$race_sim == "Black or African American"))
indian_sim_count <- length(which(dat_sim$race_sim == "American Indian or Alaska Native"))
asian_sim_count <- length(which(dat_sim$race_sim == "Asian"))
islander_sim_count <- length(which(dat_sim$race_sim == "Native Hawaiian or Pacific Islander"))

# recode income factors from (1, 13) to (Less than $10,000, $10,000 - $19,999, $20,000 - $29,999, $30,000 - $39,999, $40,000 - $49,999, $50,000 - $59,999, $60,000 - $69,999, $70,000 - $79,999, $80,000 - $89,999, $90,000 - $99,999, $100,000 - $149,999, More than $150,000, Prefer not to say) 
dat_sim <- mutate(dat_sim, income_sim = factor(income_sim, levels = c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13), 
                                           labels = c("Less than $10,000", "$10,000 - $19,999", "$20,000 - $29,999", "$30,000 - $39,999", "$40,000 - $49,999", "$50,000 - $59,999", "$60,000 - $69,999", "$70,000 - $79,999", "$80,000 - $89,999", "$90,000 - $99,999", "$100,000 - $149,999", "More than $150,000", "Prefer not to say")))
summarytools::freq(dat_sim$income_sim)

# income: creating object for percent, to include in descriptives and the table
inc_00_sim_percent <- round((nrow(filter(dat_sim, income_sim == "Less than $10,000"))/(nrow(dat_sim)) * 100), 2)
inc_01_sim_percent <- round((nrow(filter(dat_sim, income_sim == "$10,000 - $19,999"))/(nrow(dat_sim)) * 100), 2)
inc_02_sim_percent <- round((nrow(filter(dat_sim, income_sim == "$20,000 - $29,999"))/(nrow(dat_sim)) * 100), 2)
inc_03_sim_percent <- round((nrow(filter(dat_sim, income_sim == "$30,000 - $39,999"))/(nrow(dat_sim)) * 100), 2)
inc_04_sim_percent <- round((nrow(filter(dat_sim, income_sim == "$40,000 - $49,999"))/(nrow(dat_sim)) * 100), 2)
inc_05_sim_percent <- round((nrow(filter(dat_sim, income_sim == "$50,000 - $59,999"))/(nrow(dat_sim)) * 100), 2)
inc_06_sim_percent <- round((nrow(filter(dat_sim, income_sim == "$60,000 - $69,999"))/(nrow(dat_sim)) * 100), 2)
inc_07_sim_percent <- round((nrow(filter(dat_sim, income_sim == "$70,000 - $79,999"))/(nrow(dat_sim)) * 100), 2)
inc_08_sim_percent <- round((nrow(filter(dat_sim, income_sim == "$80,000 - $89,999"))/(nrow(dat_sim)) * 100), 2)
inc_09_sim_percent <- round((nrow(filter(dat_sim, income_sim == "$90,000 - $99,999"))/(nrow(dat_sim)) * 100), 2)
inc_10_sim_percent <- round((nrow(filter(dat_sim, income_sim == "$100,000 - $149,999"))/(nrow(dat_sim)) * 100), 2)
inc_15_sim_percent <- round((nrow(filter(dat_sim, income_sim == "More than $150,000"))/(nrow(dat_sim)) * 100), 2)
# check one of them
inc_00_sim_percent

# income: creating object for frequency, to include in the table 
inc_00_sim_count <- length(which(dat_sim$income_sim == "Less than $10,000"))
inc_01_sim_count <- length(which(dat_sim$income_sim == "$10,000 - $19,999"))
inc_02_sim_count <- length(which(dat_sim$income_sim == "$20,000 - $29,999"))
inc_03_sim_count <- length(which(dat_sim$income_sim == "$30,000 - $39,999"))
inc_04_sim_count <- length(which(dat_sim$income_sim == "$40,000 - $49,999"))
inc_05_sim_count <- length(which(dat_sim$income_sim == "$50,000 - $59,999"))
inc_06_sim_count <- length(which(dat_sim$income_sim == "$60,000 - $69,999"))
inc_07_sim_count <- length(which(dat_sim$income_sim == "$70,000 - $79,999"))
inc_08_sim_count <- length(which(dat_sim$income_sim == "$80,000 - $89,999"))
inc_09_sim_count <- length(which(dat_sim$income_sim == "$90,000 - $99,999"))
inc_10_sim_count <- length(which(dat_sim$income_sim == "$100,000 - $149,999"))
inc_15_sim_count <- length(which(dat_sim$income_sim == "More than $150,000"))
# check one of them
inc_00_sim_count

# recode edu factors from (1, 8) to (Less than high school, High school graduate, Some college, 2 year degree, 4 year degree, Professional degree, Doctorate, Prefer not to say)
dat_sim <- mutate(dat_sim, edu_sim = factor(edu_sim, levels = c(1, 2, 3, 4, 5, 6, 7, 8), 
                                           labels = c("Less than high school", "High school graduate", "Some college", "2 year degree", "4 year degree", "Professional degree", "Doctorate", "Prefer not to say")))
summarytools::freq(dat_sim$edu_sim)

# edu: creating object for percent, to include in descriptives and the table
l_h_sim_percent <- round((nrow(filter(dat_sim, edu_sim == "Less than high school"))/(nrow(dat_sim)) * 100), 2) 
h_s_sim_percent <- round((nrow(filter(dat_sim, edu_sim == "High school graduate"))/(nrow(dat_sim)) * 100), 2) 
s_c_sim_percent <- round((nrow(filter(dat_sim, edu_sim == "Some college"))/(nrow(dat_sim)) * 100), 2) 
twoy_sim_percent <- round((nrow(filter(dat_sim, edu_sim == "2 year degree"))/(nrow(dat_sim)) * 100), 2) 
foury_sim_percent <- round((nrow(filter(dat_sim, edu_sim == "4 year degree"))/(nrow(dat_sim)) * 100), 2) 
prof_sim_percent <- round((nrow(filter(dat_sim, edu_sim == "Professional degree"))/(nrow(dat_sim)) * 100), 2) 
doc_sim_percent <- round((nrow(filter(dat_sim, edu_sim == "Doctorate"))/(nrow(dat_sim)) * 100), 2) 
# check one of them
l_h_sim_percent 

# edu: creating object for frequency, to include in the table 
l_h_sim_count <- length(which(dat_sim$edu_sim == "Less than high school"))
h_s_sim_count <- length(which(dat_sim$edu_sim == "High school graduate"))
s_c_sim_count <- length(which(dat_sim$edu_sim == "Some college"))
twoy_sim_count <- length(which(dat_sim$edu_sim == "2 year degree"))
foury_sim_count <- length(which(dat_sim$edu_sim == "4 year degree"))
prof_sim_count <- length(which(dat_sim$edu_sim == "Professional degree"))
doc_sim_count <- length(which(dat_sim$edu_sim == "Doctorate"))
# check one of them
doc_sim_count 

```

The total sample in the current study consists of `r nrow(dat_sim)` US adults recruited from Amazon MTurk ($M_{\text{age}}$ = `r age_sim_mean`, $SD_{\text{age}}$ = `r age_sim_sd`). They were evenly assigned to one of the two conditions. The experiment begins with a consent process, followed by participants interacting with the stimuli, and then an online questionnaire including measures of variables and demographic questions. The questionnaire also includes measures of graphic qualities to ensure differences in these qualities between the two groups are not significant, and three focus questions to ensure participants answer the questions with their focus.

The eligibility criteria of participants include being adults, living in the US, being comfortable speaking English, and having access to a laptop and the Internet to complete the tasks and survey using a web browser. Each participant is compensated with a \$25 Amazon gift card.

Here is a table of the detailed breakdown of participants' demographic information:

```{r demographics table, echo=FALSE}

# this code creates a table, in which you almost literally "create" the table with the code
# that is, the first row (with the ~) serves as the column headers
# then the following entries indicate what should go in each cell. 

demo_sim_table <- dplyr::tribble(
    ~Item, ~Category, ~Frequency, ~Percentage, 
    "Gender", "Female", female_sim_count, female_sim_percent, 
    "", "Male", male_sim_count, male_sim_percent, 
    "", "Non-binary or third gender", nonbin_sim_count, nonbin_sim_percent, 
    "Race", "White", white_sim_count, white_sim_percent, 
    "", "Black or African American", black_sim_count, black_sim_percent, 
    "", "American Indian or Alaska Native", indian_sim_count, indian_sim_percent, 
    "", "Asian", asian_sim_count, asian_sim_percent, 
    "", "Native Hawaiian or Pacific Islander", islander_sim_count, islander_sim_percent, 
    "Income", "Less than $10,000", inc_00_sim_count, inc_00_sim_percent, 
    "", "$10,000 - $19,999", inc_01_sim_count, inc_01_sim_percent, 
    "", "$20,000 - $29,999", inc_02_sim_count, inc_02_sim_percent, 
    "", "$30,000 - $39,999", inc_03_sim_count, inc_03_sim_percent, 
    "", "$40,000 - $49,999", inc_04_sim_count, inc_04_sim_percent, 
    "", "$50,000 - $59,999", inc_05_sim_count, inc_05_sim_percent, 
    "", "$60,000 - $69,999", inc_06_sim_count, inc_06_sim_percent, 
    "", "$70,000 - $79,999", inc_07_sim_count, inc_07_sim_percent, 
    "", "$80,000 - $89,999", inc_08_sim_count, inc_08_sim_percent, 
    "", "$90,000 - $99,999", inc_09_sim_count, inc_09_sim_percent, 
    "", "$100,000 - $149,999", inc_10_sim_count, inc_10_sim_percent, 
    "", "More than $150,000", inc_15_sim_count, inc_15_sim_percent, 
    "Education", "Less than high school", l_h_sim_count, l_h_sim_percent, 
    "", "High school graduate", h_s_sim_count, h_s_sim_percent, 
    "", "2 year degree", twoy_sim_count, twoy_sim_percent, 
    "", "4 year degree", foury_sim_count, foury_sim_percent, 
    "", "Professional degree", prof_sim_count, prof_sim_percent, 
    "", "Doctorate", doc_sim_count, doc_sim_percent 
    )

# add the "%" sign to the third column
demo_sim_table <- demo_sim_table %>% 
  dplyr::mutate(Percentage = paste0(Percentage, "%"))

# now we can use the built in APA table function to format that table

apa_table(demo_sim_table, 
             caption = "Demographic Breakdowns of Participants",
             align = "l", digits = 2,
          longtable = TRUE, # for page break
          # note = "Demographic Breakdowns of Participants" # not in use
          )

```

## Measures

### Perceived Graphics Quality.

```{r graphics quality, include=FALSE}

# first need to re-code the scale to allocate the correct numbers (for reversed items)

dat_sim <- dat_sim %>% mutate(graphi_1_sim_scored = recode(graphi_1_sim, `1` = 1, `2` = 2, `3` = 3, `4` = 4, `5` = 5, `6` = 6, `7` = 7),
                      graphi_2_sim_scored = recode(graphi_2_sim, `1` = 1, `2` = 2, `3` = 3, `4` = 4, `5` = 5, `6` = 6, `7` = 7),
                      graphi_3_sim_scored = recode(graphi_3_sim, `1` = 1, `2` = 2, `3` = 3, `4` = 4, `5` = 5, `6` = 6, `7` = 7))

# pull these together into an object for further use

graphi_sim_items <- c("graphi_1_sim_scored", "graphi_2_sim_scored", "graphi_3_sim_scored")

# creating a new variable that is the mean score across items

dat_sim <- dat_sim %>% dplyr::mutate(graphi_sim_mean = rowMeans(dat_sim[ ,graphi_sim_items], na.rm = TRUE))

# give that new variable a label

labelled::var_label(dat_sim$graphi_sim_mean) <- "Graphics Quality Scale - Mean"

# check that all looks ok

psych::describe(dat_sim$graphi_sim_mean)

# get cronbach's alpha for the scale, assign to object

alpha_graphi_sim <-  psych::alpha(dplyr::select(dat_sim, "graphi_1_sim_scored", "graphi_2_sim_scored", "graphi_3_sim_scored"))
alpha_graphi_sim

# pull out just the alpha and save as object to insert into text
## Issue here: in the future, I should try to simulate correlated data, instead of independent items (negative alpha value)

graphi_sim_alpha <- alpha_graphi_sim$total$std.alpha
graphi_sim_alpha

# create object for mean and sd for full scale to insert into text

graphi_sim_mean <- mean(dat_sim$graphi_sim_mean)
graphi_sim_sd <- sd(dat_sim$graphi_sim_mean)
graphi_sim_mean
graphi_sim_sd

# create object for mean and sd for each group to insert into table

graphi_sim_mean_g1 <- mean(dat_sim$graphi_sim_mean[dat_sim$group_sim == 1])
graphi_sim_mean_g2 <- mean(dat_sim$graphi_sim_mean[dat_sim$group_sim == 2])
graphi_sim_sd_g1 <- sd(dat_sim$graphi_sim_mean[dat_sim$group_sim == 1])
graphi_sim_sd_g2 <- sd(dat_sim$graphi_sim_mean[dat_sim$group_sim == 2])

# create object for mean and sd for each item to insert into table

graphi_1_sim_mean <- mean(dat_sim$graphi_1_sim_scored)
graphi_2_sim_mean <- mean(dat_sim$graphi_2_sim_scored)
graphi_3_sim_mean <- mean(dat_sim$graphi_3_sim_scored)
graphi_1_sim_mean

# label each item in scale....may or may not use, but good to have

labelled::var_label(dat_sim$graphi_1_sim_scored) <- "The graphics quality of the video was clear and sharp. 1=Strongly Disagree, and 7=Strongly Agree."
labelled::var_label(dat_sim$graphi_2_sim_scored) <- "The video looked photo-realistic. 1=Strongly Disagree, and 7=Strongly Agree."
labelled::var_label(dat_sim$graphi_3_sim_scored) <- "The video looked realistic. 1=Strongly Disagree, and 7=Strongly Agree."

```

As a manipulation check, participants completed a three-item, 7-point Likert scale [@kang2020], which assessed their perceived graphics quality (Cronbach's alpha = `r round(graphi_sim_alpha, digits = 2)`).

### Perceived Interactivity.

```{r interactivity, include=FALSE}

# first need to re-code the scale to allocate the correct numbers (for reversed items)

dat_sim <- dat_sim %>% mutate(inte_1_sim_scored = recode(inte_1_sim, `1` = 1, `2` = 2, `3` = 3, `4` = 4, `5` = 5, `6` = 6, `7` = 7),
                      inte_2_sim_scored = recode(inte_2_sim, `1` = 1, `2` = 2, `3` = 3, `4` = 4, `5` = 5, `6` = 6, `7` = 7),
                      inte_3_sim_scored = recode(inte_3_sim, `1` = 1, `2` = 2, `3` = 3, `4` = 4, `5` = 5, `6` = 6, `7` = 7),
                      inte_4_sim_scored = recode(inte_4_sim, `1` = 1, `2` = 2, `3` = 3, `4` = 4, `5` = 5, `6` = 6, `7` = 7),
                      inte_5_sim_scored = recode(inte_5_sim, `1` = 1, `2` = 2, `3` = 3, `4` = 4, `5` = 5, `6` = 6, `7` = 7),
                      )

# pull these together into an object for further use

inte_sim_items <- c("inte_1_sim_scored", "inte_2_sim_scored", "inte_3_sim_scored", "inte_4_sim_scored", "inte_5_sim_scored")

# creating a new variable that is the mean score across items

dat_sim <- dat_sim %>% dplyr::mutate(inte_sim_mean = rowMeans(dat_sim[ ,inte_sim_items], na.rm = TRUE))

# give that new variable a label

labelled::var_label(dat_sim$inte_sim_mean) <- "Perceived Interactivity Scale - Mean"

# check that all looks ok

psych::describe(dat_sim$inte_sim_mean)

# get Cronbach's alpha for the scale, assign to object

alpha_inte_sim <- psych::alpha(dplyr::select(dat_sim, "inte_1_sim_scored", "inte_2_sim_scored", "inte_3_sim_scored", "inte_4_sim_scored", "inte_5_sim_scored"))
alpha_inte_sim

# pull out just the alpha and save as object to insert into text
## Issue here: in the future, I should try to simulate correlated data, instead of independent items (negative alpha value)

inte_sim_alpha <- alpha_inte_sim$total$std.alpha
inte_sim_alpha

# create object for mean and sd for full scale to insert into text

inte_sim_mean <- mean(dat_sim$inte_sim_mean)
inte_sim_sd <- sd(dat_sim$inte_sim_mean)
inte_sim_mean
inte_sim_sd

# create object for mean and sd for each group to insert into text

inte_sim_mean_g1 <- mean(dat_sim$inte_sim_mean[dat_sim$group_sim == 1])
inte_sim_sd_g1 <- sd(dat_sim$inte_sim_mean[dat_sim$group_sim == 1])
inte_sim_mean_g2 <- mean(dat_sim$inte_sim_mean[dat_sim$group_sim == 2])
inte_sim_sd_g2 <- sd(dat_sim$inte_sim_mean[dat_sim$group_sim == 2])
inte_sim_mean_g1
inte_sim_mean_g2

# create object for mean and sd for each item to insert into table

inte_1_sim_mean <- mean(dat_sim$inte_1_sim_scored)
inte_2_sim_mean <- mean(dat_sim$inte_2_sim_scored)
inte_3_sim_mean <- mean(dat_sim$inte_3_sim_scored)
inte_4_sim_mean <- mean(dat_sim$inte_4_sim_scored)
inte_5_sim_mean <- mean(dat_sim$inte_5_sim_scored)
inte_1_sim_mean

# label each item in scale....may or may not use, but good to have

labelled::var_label(dat_sim$inte_1_sim_scored) <- "I was in control of my navigation through this video. 1=Strongly Disagree, and 7=Strongly Agree."
labelled::var_label(dat_sim$inte_2_sim_scored) <- "I had some control over the content of this video. 1=Strongly Disagree, and 7=Strongly Agree."
labelled::var_label(dat_sim$inte_3_sim_scored) <- "I was able to interact with this video. 1=Strongly Disagree, and 7=Strongly Agree."
labelled::var_label(dat_sim$inte_4_sim_scored) <- "The content of this video was responsive to my interaction. 1=Strongly Disagree, and 7=Strongly Agree."
labelled::var_label(dat_sim$inte_5_sim_scored) <- "I could understand the context of this video in an interactive way. 1=Strongly Disagree, and 7=Strongly Agree."

```

Participants completed a five-item, 7-point Likert scale [@yim2017; @wu2005], which assessed their perceived interactivity (Cronbach's alpha = `r round(inte_sim_alpha, digits = 2)`).

### Social Presence.

```{r social presence, include=FALSE}

# first need to re-code the scale to allocate the correct numbers (for reversed items)

dat_sim <- dat_sim %>% mutate(soci_1_sim_scored = recode(soci_1_sim, `1` = 1, `2` = 2, `3` = 3, `4` = 4, `5` = 5, `6` = 6, `7` = 7),
                      soci_2_sim_scored = recode(soci_2_sim, `1` = 1, `2` = 2, `3` = 3, `4` = 4, `5` = 5, `6` = 6, `7` = 7),
                      soci_3_sim_scored = recode(soci_3_sim, `1` = 7, `2` = 6, `3` = 5, `4` = 4, `5` = 3, `6` = 2, `7` = 1),
                      soci_4_sim_scored = recode(soci_4_sim, `1` = 1, `2` = 2, `3` = 3, `4` = 4, `5` = 5, `6` = 6, `7` = 7),
                      soci_5_sim_scored = recode(soci_5_sim, `1` = 7, `2` = 6, `3` = 5, `4` = 4, `5` = 3, `6` = 2, `7` = 1)
                      )

# pull these together into an object for further use

soci_sim_items <- c("soci_1_sim_scored", "soci_2_sim_scored", "soci_3_sim_scored", "soci_4_sim_scored", "soci_5_sim_scored")

# creating a new variable that is the mean score across items

dat_sim <- dat_sim %>% dplyr::mutate(soci_sim_mean = rowMeans(dat_sim[ ,soci_sim_items], na.rm = TRUE))

# give that new variable a label

labelled::var_label(dat_sim$soci_sim_mean) <- "Social Presence Scale - Mean"

# check that all looks ok

psych::describe(dat_sim$soci_sim_mean)

# get Cronbach's alpha for the scale, assign to object

alpha_soci_sim <- psych::alpha(dplyr::select(dat_sim, "soci_1_sim_scored", "soci_2_sim_scored", "soci_3_sim_scored", "soci_4_sim_scored", "soci_5_sim_scored"))
alpha_soci_sim

# pull out just the alpha and save as object to insert into text
## Issue here: in the future, I should try to simulate correlated data, instead of independent items (negative alpha value)

soci_sim_alpha <- alpha_soci_sim$total$std.alpha
soci_sim_alpha

# create object for mean and sd for full scale to insert into text

soci_sim_mean <- mean(dat_sim$soci_sim_mean)
soci_sim_sd <- sd(dat_sim$soci_sim_mean)
soci_sim_mean
soci_sim_sd

# create object for mean and sd for each item to insert into table

soci_1_sim_mean <- mean(dat_sim$soci_1_sim_scored)
soci_2_sim_mean <- mean(dat_sim$soci_2_sim_scored)
soci_3_sim_mean <- mean(dat_sim$soci_3_sim_scored)
soci_4_sim_mean <- mean(dat_sim$soci_4_sim_scored)
soci_5_sim_mean <- mean(dat_sim$soci_5_sim_scored)
soci_1_sim_mean

# label each item in scale....may or may not use, but good to have

labelled::var_label(dat_sim$soci_1_sim_scored) <- "It feels as if this girl is present in the same space as me. 1=Strongly Disagree, and 7=Strongly Agree."
labelled::var_label(dat_sim$soci_2_sim_scored) <- "It feels as if the girl is watching me and is aware of my presence. 1=Strongly Disagree, and 7=Strongly Agree."
labelled::var_label(dat_sim$soci_3_sim_scored) <- "The thought that the girl isn't real crossed my mind often. 1=Strongly Disagree, and 7=Strongly Agree."
labelled::var_label(dat_sim$soci_4_sim_scored) <- "The girl appears to be alive. 1=Strongly Disagree, and 7=Strongly Agree."
labelled::var_label(dat_sim$soci_5_sim_scored) <- "The girl is only a computerized image, not a real person. 1=Strongly Disagree, and 7=Strongly Agree."

```

Participants completed a ten-item, 7-point Likert scale [@higgins2022], which assessed their social presence (Cronbach's alpha = `r round(soci_sim_alpha, digits = 2)`).

### Sympathy.

```{r sympathy, include=FALSE}

# first need to re-code the scale to allocate the correct numbers (for reversed items)

dat_sim <- dat_sim %>% mutate(symp_1_sim_scored = recode(symp_1_sim, `1` = 1, `2` = 2, `3` = 3, `4` = 4, `5` = 5, `6` = 6, `7` = 7),
                      symp_2_sim_scored = recode(symp_2_sim, `1` = 1, `2` = 2, `3` = 3, `4` = 4, `5` = 5, `6` = 6, `7` = 7),
                      symp_3_sim_scored = recode(symp_3_sim, `1` = 1, `2` = 2, `3` = 3, `4` = 4, `5` = 5, `6` = 6, `7` = 7),
                      symp_4_sim_scored = recode(symp_4_sim, `1` = 1, `2` = 2, `3` = 3, `4` = 4, `5` = 5, `6` = 6, `7` = 7),
                      symp_5_sim_scored = recode(symp_5_sim, `1` = 1, `2` = 2, `3` = 3, `4` = 4, `5` = 5, `6` = 6, `7` = 7),
                      symp_6_sim_scored = recode(symp_6_sim, `1` = 1, `2` = 2, `3` = 3, `4` = 4, `5` = 5, `6` = 6, `7` = 7),
                      symp_7_sim_scored = recode(symp_7_sim, `1` = 1, `2` = 2, `3` = 3, `4` = 4, `5` = 5, `6` = 6, `7` = 7),
                      symp_8_sim_scored = recode(symp_8_sim, `1` = 1, `2` = 2, `3` = 3, `4` = 4, `5` = 5, `6` = 6, `7` = 7),
                      symp_9_sim_scored = recode(symp_9_sim, `1` = 1, `2` = 2, `3` = 3, `4` = 4, `5` = 5, `6` = 6, `7` = 7),
                      symp_10_sim_scored = recode(symp_10_sim, `1` = 1, `2` = 2, `3` = 3, `4` = 4, `5` = 5, `6` = 6, `7` = 7)
                      )

# pull these together into an object for further use

symp_sim_items <- c("symp_1_sim_scored", "symp_2_sim_scored", "symp_3_sim_scored", "symp_4_sim_scored", "symp_5_sim_scored", "symp_6_sim_scored", "symp_7_sim_scored", "symp_8_sim_scored", "symp_9_sim_scored", "symp_10_sim_scored")

# creating a new variable that is the mean score across items

dat_sim <- dat_sim %>% dplyr::mutate(symp_sim_mean = rowMeans(dat_sim[ ,symp_sim_items], na.rm = TRUE))

# give that new variable a label

labelled::var_label(dat_sim$symp_sim_mean) <- "Sympathy Scale - Mean"

# check that all looks ok

psych::describe(dat_sim$symp_sim_mean)

# get Cronbach's alpha for the scale, assign to object

alpha_symp_sim <- psych::alpha(dplyr::select(dat_sim, "symp_1_sim_scored", "symp_2_sim_scored", "symp_3_sim_scored", "symp_4_sim_scored", "symp_5_sim_scored", "symp_6_sim_scored", "symp_7_sim_scored", "symp_8_sim_scored", "symp_9_sim_scored", "symp_10_sim_scored"))
alpha_symp_sim

# pull out just the alpha and save as object to insert into text
## Issue here: in the future, I should try to simulate correlated data, instead of independent items (negative alpha value)

symp_sim_alpha <- alpha_symp_sim$total$std.alpha
symp_sim_alpha

# create object for mean and sd for full scale to insert into text

symp_sim_mean <- mean(dat_sim$symp_sim_mean)
symp_sim_sd <- sd(dat_sim$symp_sim_mean)
symp_sim_mean
symp_sim_sd

# create object for mean and sd for each item to insert into table

symp_1_sim_mean <- mean(dat_sim$symp_1_sim_scored)
symp_2_sim_mean <- mean(dat_sim$symp_2_sim_scored)
symp_3_sim_mean <- mean(dat_sim$symp_3_sim_scored)
symp_4_sim_mean <- mean(dat_sim$symp_4_sim_scored)
symp_5_sim_mean <- mean(dat_sim$symp_5_sim_scored)
symp_6_sim_mean <- mean(dat_sim$symp_6_sim_scored)
symp_7_sim_mean <- mean(dat_sim$symp_7_sim_scored)
symp_8_sim_mean <- mean(dat_sim$symp_8_sim_scored)
symp_9_sim_mean <- mean(dat_sim$symp_9_sim_scored)
symp_10_sim_mean <- mean(dat_sim$symp_10_sim_scored)
symp_1_sim_mean

# label each item in scale....may or may not use, but good to have

labelled::var_label(dat_sim$symp_1_sim_scored) <- "While watching this advertisement, I feel upset. 1=Strongly Disagree, and 7=Strongly Agree."
labelled::var_label(dat_sim$symp_2_sim_scored) <- "While watching this advertisement, I feel distressed. 1=Strongly Disagree, and 7=Strongly Agree."
labelled::var_label(dat_sim$symp_3_sim_scored) <- "While watching this advertisement, I feel sympathetic. 1=Strongly Disagree, and 7=Strongly Agree."
labelled::var_label(dat_sim$symp_4_sim_scored) <- "While watching this advertisement, I feel alarmed. 1=Strongly Disagree, and 7=Strongly Agree."
labelled::var_label(dat_sim$symp_5_sim_scored) <- "While watching this advertisement, I feel grieved. 1=Strongly Disagree, and 7=Strongly Agree."
labelled::var_label(dat_sim$symp_6_sim_scored) <- "While watching this advertisement, I feel troubled. 1=Strongly Disagree, and 7=Strongly Agree."
labelled::var_label(dat_sim$symp_7_sim_scored) <- "While watching this advertisement, I feel compassionate. 1=Strongly Disagree, and 7=Strongly Agree."
labelled::var_label(dat_sim$symp_8_sim_scored) <- "While watching this advertisement, I feel perturbed. 1=Strongly Disagree, and 7=Strongly Agree."
labelled::var_label(dat_sim$symp_9_sim_scored) <- "While watching this advertisement, I feel worried. 1=Strongly Disagree, and 7=Strongly Agree."
labelled::var_label(dat_sim$symp_10_sim_scored) <- "While watching this advertisement, I feel disturbed. 1=Strongly Disagree, and 7=Strongly Agree."

```

Participants completed a 10-item, 7-point Likert scale [@baberini2015], which assessed their sympathy (Cronbach's alpha = `r round(symp_sim_alpha, digits = 2)`).

### Perceived Playfulness.

```{r perceived playfulness, include=FALSE}

# first need to re-code the scale to allocate the correct numbers (for reversed items)

dat_sim <- dat_sim %>% mutate(play_1_sim_scored = recode(play_1_sim, `1` = 1, `2` = 2, `3` = 3, `4` = 4, `5` = 5, `6` = 6, `7` = 7),
                      play_2_sim_scored = recode(play_2_sim, `1` = 1, `2` = 2, `3` = 3, `4` = 4, `5` = 5, `6` = 6, `7` = 7),
                      play_3_sim_scored = recode(play_3_sim, `1` = 1, `2` = 2, `3` = 3, `4` = 4, `5` = 5, `6` = 6, `7` = 7),
                      play_4_sim_scored = recode(play_4_sim, `1` = 1, `2` = 2, `3` = 3, `4` = 4, `5` = 5, `6` = 6, `7` = 7)
                      )

# pull these together into an object for further use

play_sim_items <- c("play_1_sim_scored", "play_2_sim_scored", "play_3_sim_scored", "play_4_sim_scored")

# creating a new variable that is the mean score across items

dat_sim <- dat_sim %>% dplyr::mutate(play_sim_mean = rowMeans(dat_sim[ ,play_sim_items], na.rm = TRUE))

# give that new variable a label

labelled::var_label(dat_sim$play_sim_mean) <- "Perceived Playfulness Scale - Mean"

# check that all looks ok

psych::describe(dat_sim$play_sim_mean)

# get Cronbach's alpha for the scale, assign to object

alpha_play_sim <- psych::alpha(dplyr::select(dat_sim, "play_1_sim_scored", "play_2_sim_scored", "play_3_sim_scored", "play_4_sim_scored"))
alpha_play_sim

# pull out just the alpha and save as object to insert into text

play_sim_alpha <- alpha_play_sim$total$std.alpha
play_sim_alpha

# create object for mean and sd for full scale to insert into text

play_sim_mean <- mean(dat_sim$play_sim_mean)
play_sim_sd <- sd(dat_sim$play_sim_mean)
play_sim_mean
play_sim_sd

# create object for mean and sd for each item to insert into table

play_1_sim_mean <- mean(dat_sim$play_1_sim_scored)
play_2_sim_mean <- mean(dat_sim$play_2_sim_scored)
play_3_sim_mean <- mean(dat_sim$play_3_sim_scored)
play_4_sim_mean <- mean(dat_sim$play_4_sim_scored)
play_1_sim_mean

# label each item in scale....may or may not use, but good to have

labelled::var_label(dat_sim$play_1_sim_scored) <- "I find this advertisement enjoyable. 1=Strongly Disagree, and 7=Strongly Agree."
labelled::var_label(dat_sim$play_2_sim_scored) <- "I find this advertisement exciting. 1=Strongly Disagree, and 7=Strongly Agree."
labelled::var_label(dat_sim$play_3_sim_scored) <- "I find this advertisement fun. 1=Strongly Disagree, and 7=Strongly Agree."
labelled::var_label(dat_sim$play_4_sim_scored) <- "I find this advertisement makes me feel like I am in another world. 1=Strongly Disagree, and 7=Strongly Agree."

```

Participants completed a four-item, 7-point Likert scale [@kang2020], which assessed their perceived playfulness (Cronbach's alpha = `r round(play_sim_alpha, digits = 2)`).

### Perceived Response Efficacy.

```{r perceived response efficacy, include=FALSE}

# first need to re-code the scale to allocate the correct numbers (for reversed items)

dat_sim <- dat_sim %>% mutate(effi_1_sim_scored = recode(effi_1_sim, `1` = 1, `2` = 2, `3` = 3, `4` = 4, `5` = 5, `6` = 6, `7` = 7),
                      effi_2_sim_scored = recode(effi_2_sim, `1` = 1, `2` = 2, `3` = 3, `4` = 4, `5` = 5, `6` = 6, `7` = 7),
                      effi_3_sim_scored = recode(effi_3_sim, `1` = 1, `2` = 2, `3` = 3, `4` = 4, `5` = 5, `6` = 6, `7` = 7),
                      effi_4_sim_scored = recode(effi_4_sim, `1` = 1, `2` = 2, `3` = 3, `4` = 4, `5` = 5, `6` = 6, `7` = 7)
                      )

# pull these together into an object for further use

effi_sim_items <- c("effi_1_sim_scored", "effi_2_sim_scored", "effi_3_sim_scored", "effi_4_sim_scored")

# creating a new variable that is the mean score across items

dat_sim <- dat_sim %>% dplyr::mutate(effi_sim_mean = rowMeans(dat_sim[ ,effi_sim_items], na.rm = TRUE))

# give that new variable a label

labelled::var_label(dat_sim$effi_sim_mean) <- "Perceived Response Efficacy Scale - Mean"

# check that all looks ok

psych::describe(dat_sim$effi_sim_mean)

# get Cronbach's alpha for the scale, assign to object

alpha_effi_sim <- psych::alpha(dplyr::select(dat_sim, "effi_1_sim_scored", "effi_2_sim_scored", "effi_3_sim_scored", "effi_4_sim_scored"))
alpha_effi_sim

# pull out just the alpha and save as object to insert into text

effi_sim_alpha <- alpha_effi_sim$total$std.alpha
effi_sim_alpha

# create object for mean and sd for full scale to insert into text

effi_sim_mean <- mean(dat_sim$effi_sim_mean)
effi_sim_sd <- sd(dat_sim$effi_sim_mean)
effi_sim_mean
effi_sim_sd

# create object for mean and sd for each item to insert into table

effi_1_sim_mean <- mean(dat_sim$effi_1_sim_scored)
effi_2_sim_mean <- mean(dat_sim$effi_2_sim_scored)
effi_3_sim_mean <- mean(dat_sim$effi_3_sim_scored)
effi_4_sim_mean <- mean(dat_sim$effi_4_sim_scored)
effi_1_sim_mean

# label each item in scale....may or may not use, but good to have

labelled::var_label(dat_sim$effi_1_sim_scored) <- "My donation will make a positive difference. 1=Strongly Disagree, and 7=Strongly Agree."
labelled::var_label(dat_sim$effi_2_sim_scored) <- "Donations to this advertisement will make a meaningful difference. 1=Strongly Disagree, and 7=Strongly Agree."
labelled::var_label(dat_sim$effi_3_sim_scored) <- "It is valuable to make a donation to this advertisement. 1=Strongly Disagree, and 7=Strongly Agree."
labelled::var_label(dat_sim$effi_4_sim_scored) <- "Donations to this advertisement will have impact. 1=Strongly Disagree, and 7=Strongly Agree."

```

Participants completed a four-item, 7-point Likert scale [@cryder2013; @sharma2016], which assessed their perceived response efficacy (Cronbach's alpha = `r round(effi_sim_alpha, digits = 2)`).

### Donation Intention.

```{r donation intention, include=FALSE}

# first need to re-code the scale to allocate the correct numbers (for reversed items)

dat_sim <- dat_sim %>% mutate(dona_1_sim_scored = recode(dona_1_sim, `1` = 1, `2` = 2, `3` = 3, `4` = 4, `5` = 5, `6` = 6, `7` = 7),
                      dona_2_sim_scored = recode(dona_2_sim, `1` = 1, `2` = 2, `3` = 3, `4` = 4, `5` = 5, `6` = 6, `7` = 7),
                      dona_3_sim_scored = recode(dona_3_sim, `1` = 1, `2` = 2, `3` = 3, `4` = 4, `5` = 5, `6` = 6, `7` = 7)
                      )

# pull these together into an object for further use

dona_sim_items <- c("dona_1_sim_scored", "dona_2_sim_scored", "dona_3_sim_scored")

# creating a new variable that is the mean score across items

dat_sim <- dat_sim %>% dplyr::mutate(dona_sim_mean = rowMeans(dat_sim[ ,dona_sim_items], na.rm = TRUE))

# give that new variable a label

labelled::var_label(dat_sim$dona_sim_mean) <- "Donation Intention Scale - Mean"

# check that all looks ok

psych::describe(dat_sim$dona_sim_mean)

# get Cronbach's alpha for the scale, assign to object

alpha_dona_sim <- psych::alpha(dplyr::select(dat_sim, "dona_1_sim_scored", "dona_2_sim_scored", "dona_3_sim_scored"))
alpha_dona_sim

# pull out just the alpha and save as object to insert into text

dona_sim_alpha <- alpha_dona_sim$total$std.alpha
dona_sim_alpha

# create object for mean and sd for full scale to insert into text

dona_sim_mean <- mean(dat_sim$dona_sim_mean)
dona_sim_sd <- sd(dat_sim$dona_sim_mean)
dona_sim_mean
dona_sim_sd

# create object for mean and sd for each item to insert into table

dona_1_sim_mean <- mean(dat_sim$dona_1_sim_scored)
dona_2_sim_mean <- mean(dat_sim$dona_2_sim_scored)
dona_3_sim_mean <- mean(dat_sim$dona_3_sim_scored)
dona_1_sim_mean

# label each item in scale....may or may not use, but good to have

labelled::var_label(dat_sim$dona_1_sim_scored) <- "How motivated would you be to after watching the video? 1=Not at all motivated, and 7=Extremely motivated."
labelled::var_label(dat_sim$dona_2_sim_scored) <- "I intend to help in the situation depicted in the advertisement. 1=Strongly Disagree, and 7=Strongly Agree."
labelled::var_label(dat_sim$dona_3_sim_scored) <- "How willing would you be to donate for this advertisement? 1=Extremely unwilling, and 7=Extremely willing."

```

Participants completed a three-item, 7-point Likert scale [@li2022], which assessed their donation intention (Cronbach's alpha = `r round(dona_sim_alpha, digits = 2)`).

## Data analysis

We used `r cite_r("r-references.bib")` for all our analyses.

# Results

## Manipulation Tests

```{r graphi t-test, include=FALSE}

# F-test to compare two variances (homogeneity of variance)
# Remove this part because the default t-test in R is Welch's, for unequal variances.
# var.test(dat_sim$graphi_sim_mean ~ dat_sim$group_sim) # the variances are not significantly different

# comparing graphic quality between two groups (graphics quality)
t_test_graphi_sim <- t.test(dat_sim$graphi_sim_mean ~ dat_sim$group_sim)
t_test_graphi_sim

# save out all necessary objects

t_graphi_sim <- round(t_test_graphi_sim$statistic, 2)
df_graphi_sim <- round(t_test_graphi_sim$parameter, 2)

# correctly format the p-value using printp()
p_graphi_sim_fmt <- printp(t_test_graphi_sim$p.value)

p_graphi_sim_fmt
  
```

Overall, the graphic quality of the stimuli for two participant groups is well perceived ($M_{\text{graphic quality}}$ = `r round(graphi_sim_mean, digits = 2)`, $SD_{\text{graphic quality}}$ = `r round(graphi_sim_sd, digits = 2)`). The results from a Welch's independent samples *t*-test indicated no significant differences between the two groups, *t*(`r df_graphi_sim`) = `r t_graphi_sim`, *p* = `r p_graphi_sim_fmt` (see Figure \@ref(fig:graphi-graph)).

```{r graphi-graph, echo=FALSE, fig.cap="Perceived graphic quality of stimuli.", fig.width = 6.5, fig.height = 3.7, dpi = 300}
# ggplot: update the chart to a Boxplot + a Jitter to reveal the median, quartiles, and the actual raw data points
# orginal version: a bar chart with error bars, which is not the best choice
# reference link: https://simplystatistics.org/posts/2019-02-21-dynamite-plots-must-die/

# prepare data for ggplot: group labels
dat_sim$group_label <- factor(dat_sim$group_sim, 
                              levels = c(1, 2), 
                              labels = c("High interactivity", "Low interactivity")) 

# create ggplot boxplot + jitter
ggplot(dat_sim, aes(x = group_label, y = graphi_sim_mean, fill = group_label)) +
  
  # Add the boxplot
  geom_boxplot(width = 0.5, alpha = 0.6) +
  
  # Add the jittered points
  geom_jitter(width = 0.1, height = 0, size = 1.5, alpha = 0.6) +
  
  scale_fill_manual(
    values = c("Low interactivity"  = "#1b9e77",
               "High interactivity" = "#d95f02")
  ) +
  
  scale_x_discrete(name = "Groups") +
  scale_y_continuous(
    name = "Perceived graphic quality",
    breaks = 1:7,
    expand = c(0, 0)
  ) + 
  
  coord_cartesian(ylim = c(0.5, 7.5)) +
  
  theme_apa() +
  theme(legend.position = "none")

```

```{r interactivity-t-test, include=FALSE}

# F-test to compare two variances (homogeneity of variance)
# Remove this part because the default t-test in R is Welch's, for unequal variances.
# var.test(dat_sim$inte_sim_mean ~ dat_sim$group_sim) # the variances are not significantly different

# comparing graphic quality between two groups (interactivity)
t_test_inte_sim <- t.test(dat_sim$inte_sim_mean ~ dat_sim$group_sim)
t_test_inte_sim

# save out all necessary objects

t_inte_sim <- round(t_test_inte_sim$statistic, 2)
df_inte_sim <- round(t_test_inte_sim$parameter, 2)

# correctly format the p-value using printp()
p_inte_sim_fmt <- printp(t_test_inte_sim$p.value)
p_inte_sim_fmt
  
```

According to the results from a Welch's independent samples *t*-test that compares the perceived interactivity of the stimuli between the high-interactivity group ($M_{\text{high interactivity}}$ = `r round(inte_sim_mean_g1, digits = 2)`, $SD_{\text{high interactivity}}$ = `r round(inte_sim_sd_g1, digits = 2)`) and the low-interactivity group ($M_{\text{low interactivity}}$ = `r round(inte_sim_mean_g2, digits = 2)`, $SD_{\text{low interactivity}}$ = `r round(inte_sim_sd_g2, digits = 2)`), there are significant differences between the two groups, *t*(`r df_inte_sim`) = `r t_inte_sim`, *p* `r p_inte_sim_fmt` (see Figure \@ref(fig:interactivity-graph)).

```{r interactivity-graph, fig.cap="Perceived interactivity of stimuli.", echo=FALSE, fig.width = 6.5, fig.height = 3.7, dpi = 300}
# ggplot: update the chart to a Boxplot + a Jitter to reveal the median, quartiles, and the actual raw data points
# orginal version: a bar chart with error bars, which is not the best choice
# reference link: https://simplystatistics.org/posts/2019-02-21-dynamite-plots-must-die/

# prepare data for ggplot: group labels
dat_sim$group_label <- factor(dat_sim$group_sim, 
                              levels = c(1, 2), 
                              labels = c("High interactivity", "Low interactivity")) 

# create ggplot boxplot + jitter
ggplot(dat_sim, aes(x = group_label, y = inte_sim_mean, fill = group_label)) +
  
  # Add the boxplot
  geom_boxplot(width = 0.5, alpha = 0.6) +
  
  # Add the jittered points
  geom_jitter(width = 0.1, height = 0, size = 1.5, alpha = 0.6) +
  
  scale_fill_manual(
    values = c("Low interactivity"  = "#1b9e77",
               "High interactivity" = "#d95f02")
  ) +
  
  scale_x_discrete(name = "Groups") +
  scale_y_continuous(
    name = "Perceived interactivity",
    breaks = 1:7,
    expand = c(0, 0)
  ) + 
  
  coord_cartesian(ylim = c(0.5, 7.5)) +
  
  theme_apa() +
  theme(legend.position = "none")

```

## Hypotheses Validation

A series of Pearson correlation tests was conducted to assess the hypotheses. All hypotheses were supported (see the table below).

```{r pearson h1a inte ~ play, include = FALSE}
# Pearson correlation test

cor_inte_play_sim <- cor.test(dat_sim$inte_sim_mean, dat_sim$play_sim_mean)
cor_inte_play_sim

# save out all necessary objects
t_inte_play_sim <- round(cor_inte_play_sim$statistic, 2)
df_inte_play_sim <- round(cor_inte_play_sim$parameter, 2)

p_inte_play_sim_fmt <- printp(cor_inte_play_sim$p.value)

```

```{r pearson h1b inte ~ symp, include = FALSE}
# Pearson correlation test

cor_inte_symp_sim <- cor.test(dat_sim$inte_sim_mean, dat_sim$symp_sim_mean)
cor_inte_symp_sim

# save out all necessary objects
t_inte_symp_sim <- round(cor_inte_symp_sim$statistic, 2)
df_inte_symp_sim <- round(cor_inte_symp_sim$parameter, 2)

p_inte_symp_sim_fmt <- printp(cor_inte_symp_sim$p.value)

```

```{r pearson h1c inte ~ soci, include = FALSE}
# Pearson correlation test

cor_inte_soci_sim <- cor.test(dat_sim$inte_sim_mean, dat_sim$soci_sim_mean)
cor_inte_soci_sim

# save out all necessary objects
t_inte_soci_sim <- round(cor_inte_soci_sim$statistic, 2)
df_inte_soci_sim <- round(cor_inte_soci_sim$parameter, 2)

p_inte_soci_sim_fmt <- printp(cor_inte_soci_sim$p.value)

```

```{r pearson h2a play ~ effi, include = FALSE}
# Pearson correlation test

cor_play_effi_sim <- cor.test(dat_sim$play_sim_mean, dat_sim$effi_sim_mean)
cor_play_effi_sim

# save out all necessary objects
t_play_effi_sim <- round(cor_play_effi_sim$statistic, 2)
df_play_effi_sim <- round(cor_play_effi_sim$parameter, 2)

p_play_effi_sim_fmt <- printp(cor_play_effi_sim$p.value)

```

```{r pearson h2b play ~ dona, include = FALSE}
# Pearson correlation test

cor_play_dona_sim <- cor.test(dat_sim$play_sim_mean, dat_sim$dona_sim_mean)
cor_play_dona_sim

# save out all necessary objects
t_play_dona_sim <- round(cor_play_dona_sim$statistic, 2)
df_play_dona_sim <- round(cor_play_dona_sim$parameter, 2)

p_play_dona_sim_fmt <- printp(cor_play_dona_sim$p.value)

```

```{r pearson h3a symp ~ effi, include = FALSE}
# Pearson correlation test

cor_symp_effi_sim <- cor.test(dat_sim$symp_sim_mean, dat_sim$effi_sim_mean)
cor_symp_effi_sim

# save out all necessary objects
t_symp_effi_sim <- round(cor_symp_effi_sim$statistic, 2)
df_symp_effi_sim <- round(cor_symp_effi_sim$parameter, 2)

p_symp_effi_sim_fmt <- printp(cor_symp_effi_sim$p.value)

```

```{r pearson h3b symp ~ dona, include = FALSE}
# Pearson correlation test

cor_symp_dona_sim <- cor.test(dat_sim$symp_sim_mean, dat_sim$dona_sim_mean)
cor_symp_dona_sim

# save out all necessary objects
t_symp_dona_sim <- round(cor_symp_dona_sim$statistic, 2)
df_symp_dona_sim <- round(cor_symp_dona_sim$parameter, 2)

p_symp_dona_sim_fmt <- printp(cor_symp_dona_sim$p.value)

```

```{r pearson h4a soci ~ effi, include = FALSE}
# Pearson correlation test

cor_soci_effi_sim <- cor.test(dat_sim$soci_sim_mean, dat_sim$effi_sim_mean)
cor_soci_effi_sim

# save out all necessary objects
t_soci_effi_sim <- round(cor_soci_effi_sim$statistic, 2)
df_soci_effi_sim <- round(cor_soci_effi_sim$parameter, 2)

p_soci_effi_sim_fmt <- printp(cor_soci_effi_sim$p.value)

```

```{r pearson h4b soci ~ dona, include = FALSE}
# Pearson correlation test

cor_soci_dona_sim <- cor.test(dat_sim$soci_sim_mean, dat_sim$dona_sim_mean)
cor_soci_dona_sim

# save out all necessary objects
t_soci_dona_sim <- round(cor_soci_dona_sim$statistic, 2)
df_soci_dona_sim <- round(cor_soci_dona_sim$parameter, 2)

p_soci_dona_sim_fmt <- printp(cor_soci_dona_sim$p.value)

```

```{r pearson h5 effi ~ dona, include = FALSE}
# Pearson correlation test

cor_effi_dona_sim <- cor.test(dat_sim$effi_sim_mean, dat_sim$dona_sim_mean)
cor_effi_dona_sim

# save out all necessary objects
t_effi_dona_sim <- round(cor_effi_dona_sim$statistic, 2)
df_effi_dona_sim <- round(cor_effi_dona_sim$parameter, 2)

p_effi_dona_sim_fmt <- printp(cor_effi_dona_sim$p.value)

```

```{r hypothesis-table, echo=FALSE}

# this code creates a table, in which you almost literally "create" the table with the code
# that is, the first row (with the ~) serves as the column headers
# then the following entries indicate what should go in each cell. 

hypo_sim_table <- dplyr::tribble(
    ~Hypothesis, ~Pairs, ~t, ~p,  
    "H1a", "Interactivity $\\leftrightarrow$ Playfulness", t_inte_play_sim, p_inte_play_sim_fmt, 
    "H1b", "Interactivity $\\leftrightarrow$ Sympathy", t_inte_symp_sim, p_inte_symp_sim_fmt, 
    "H1c", "Interactivity $\\leftrightarrow$ Social presence", t_inte_soci_sim, p_inte_soci_sim_fmt, 
    "H2a", "Playfulness $\\leftrightarrow$ Response efficacy", t_play_effi_sim, p_play_effi_sim_fmt, 
    "H2b", "Playfulness $\\leftrightarrow$ Donation intention", t_play_dona_sim, p_play_dona_sim_fmt, 
    "H3a", "Sympathy $\\leftrightarrow$ Response efficacy", t_symp_effi_sim, p_symp_effi_sim_fmt, 
    "H3b", "Sympathy $\\leftrightarrow$ Donation intention", t_symp_dona_sim, p_symp_dona_sim_fmt, 
    "H4a", "Social presence $\\leftrightarrow$ Response efficacy", t_soci_effi_sim, p_soci_effi_sim_fmt, 
    "H4b", "Social presence $\\leftrightarrow$ Donation intention", t_soci_dona_sim, p_soci_dona_sim_fmt, 
    "H5", "Response efficacy $\\leftrightarrow$ Donation intention", t_effi_dona_sim, p_effi_dona_sim_fmt
    )

# now we can use the built in APA table function to format that table

apa_table(hypo_sim_table, 
          caption = "Hypotheses Test Results",
          col.names = c("Hypothesis", "Pairs", "\\textit{t}", "\\textit{p}"), # italic column labels
          escape = FALSE, # allow LaTeX in the table
          align = "l", 
          digits = 2,
          longtable = TRUE, # for page break
          )

```

# Discussion

This study aimed to explore how perceived interactivity influences donation intention in advertisement design. The results supported our hypotheses, showing that this relationship is mediated by perceived playfulness, sympathy, social presence, and response efficacy. As a result, these findings suggest that advertisers and marketers should focus on interactive features to effectively encourage donation intentions. Future research should explore which design elements can effectively improve perceived interactivity.

\newpage

# References

::: {#refs custom-style="Bibliography"}
:::
